Solar jet observed at the limb in SDO/SST

### 2016-05-11 paper/ms_temp_paper.tex
Finish of the short STEREO section

\subsection{STEREO-A}
We are fortunate that we can observe the jet feature in the STEREO-A/EUVI, with the position of the spacecraft at approximately $90^\circ$ to the Sun-Earth line.
This facilitates the building of a larger picture of the behaviour of the jet, the downside to this however, is that with STEREO-A being at such a distance the cadence is low, $~10$ mins.
In this case we obtain 4 images in $30.4$ nm in which the jet is observed

>>>>

\subsection{STEREO-A}
We are fortunate that we can observe the jet feature in the STEREO-A/EUVI, with the position of the spacecraft at approximately $90^\circ$ to the Sun-Earth line.
This facilitates the building of a larger picture of the behaviour of the jet, the downside to this however, is that with STEREO-A being at such a distance the cadence is low, $~10$ mins.
In this case we obtain 4 images in $30.4$ nm in which the jet is observed.
The jet appears as a dark fibril like feature originating at ***A POINT IN SPACE*** and extending across the disk to a length of $45.1$arcsec.
Significantly, the component of extension in the East-West direction is not insignificant, approximately $30$ arcsec.
With this information we calculate that the total length of the feature, taking into account both SDO and STEREO's view, is $25.5$ Mm.
